Synergistic retrievals of ice in clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-05-14 RST/responseReviewers.tex

as well. Regarding the measurement uncertainties, we account for them in the radar and radiometer simulations,
and in a rather idealized way in the lidar simulations.  Specifically, we assume random errors with 0.0 mean
and 0.5dB standard deviation in the radar observations \cite{takahashi2008}, and a Noise-Equivalent-Delta-T (NEDT)
of 1K, which is a readily achievable level for modern satellite radiometers \cite{draper2015}. A complex 

@@

model of space-borne lidar measurement uncertainties was developed in \cite{liu2006}, but its parameters are
difficult to reliably quantify from theoretical considerations based on instrument expectations alone. Instead, we
assume a simple multiplicative error model, with the multiplicative factor model as a log-normally distributed random
variable with 0.0 mean and 0.1 standard deviation, which result in observation uncertainties similar to those in
the in evaluation study of the Cloud-Aerosol Transport System (CATS) lidar-system. 
We acknowledge the limitations of this approach in the manuscript.\\

@@

    AOS mission instruments, it is unclear whether thermal noise is included in the retrieval experiments. 
    The authors should mention this in the description of their methodology.}\\
\newline
Regarding the measurement uncertainties, we account for them in the radar and radiometer simulations,
and in a rather idealized way in the lidar simulations.  Specifically, we assume random errors with 0.0 mean
of 1K, which is a readily achievable level for modern satellite radiometers \cite{draper2015}.
A complex model of space-borne lidar measurement uncertainties was developed in \cite{liu2006}, but its parameters are
variable with 0.0 mean and 0.1 standard deviation, which result in observation uncertainties similar to those in
the in evaluation study of the Cloud-Aerosol Transport System (CATS) lidar-system. 
We acknowledge the limitations of this approach in the manuscript.\\ 

### 2023-05-14 RST/RSTManuscript.tex
review May 14

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use
normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they 
encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter,
i.e. the 
normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized
PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water 
content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  \cite{testud2001} showed 
that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and 
that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
perfectly explains the relationships between IWC and Z calculated from observed PSDs. 
Although the initial work of \cite{testud2001} was limited to rain and only hinted about the applicability
of the normalization concept to ice observations, subsequent studies showed that parameterizations
of type (\ref{eq:1}) extended to ice \citep{ferreira2001,delanoe2014}.
Equation (\ref{eq:1}) is not 
sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in 
time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function 
of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, 
rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize
$N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}.  
Specifically, we cluster, based on similarity, a large set 2C-ICE profiles into 18 classes using a k-Means 
procedure. The mean IWC profiles associated with the 18 classes are shown in continuous lines in Figure 1.  
Our estimates, derived using PSD assumptions and electromagnetic scattering calculations that enable 
accurate and physically consistent simulations of radar observations at Ku-band and radiometer observations of 
submillimeter-wave frequencies are also shown in Figure 1. These estimates are based on the self-similarity 
Rayleigh-Gans approximation (SSRGA) of \cite{hogan2017ssrga}. Details regarding the
estimation process are provided in the following paragraphs.  As apparent in Figure 1, the CS and SSRGA estimates are in good 
agreement.  Some discrepancies due to differences between the SSRGA $N_w$ parameterization and the CS 2C-ICE 
"a priori assumptions" are also apparent, but they are not deemed critical in this study, whose objective is 
the investigation of synergistic lidar, Ku-band radar and submillimeter-wave radiometer retrievals, because the 
outcome is not likely to be sensitive to such details.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\textwidth,angle=0]{./Figs/fig01.png}\\
    \caption{Mean CS IWC profiles for 18 classes derived using the k-Means clustering algorithm. For a 
    compressed but intelligible representation, three classes are shown in different colors in each panel.
    The associated 
    mean profiles derived from CS reflectivity observations using the SSRGA scattering calculations 
    and $N_w$ parameterization developed in this study are shown using symbol *. The vertical coordinate 
    is defined relative to the freezing level.}\label{f1}
\end{figure}

@@

For the determination of reference $a$ and $b$ values to be used with Equation (\ref{eq:1}), we assume that 
PSDs are normalized gamma  distributions with $N_w=0.08cm^{-4}$ and $\mu=2$ and calculate 
\begin{equation}
 Z=\frac {\lambda ^4} {\pi ^5 |K_w|^2} \int_0^{\infty} N(D,D_m) \sigma _b(D) dD
\end{equation}
where $\lambda$ is the radar frequency, $|K_w|$ is the dielectric factor of water, $N(D,D_m) dD$ is the number 
of ice particles of diameter with D and D+dD per unit volume, $D_m$ is the mass weighted mean diameter of the 
distribution, and $\sigma _b(D)$ is the backscattering cross-section of ice particle of diameter $D$. The mass 
weighted mean diameter is equidistantly sampled to span the entire range of IWC values in the CS 2C-ICE dataset.
The assumed mass-size relation is that of \cite{brown1995improved} because it works well with the 
SSRGA scattering calculations \citep{heymsfield2022impacts}.  The open source software scatter-1.1 of \citep{scatter-1.1}
is used to provide the actual scattering properties. The SSRGA theory was developed for millimeter and 
submillimeter-wave calculations and may not be applicable at lidar's wavelength.  
To improve the representation of microphysical variability in the study, we don't assume the values of $N_w$ given
by the 2C-ICE based parametrization described above as the true values. Instead, we perturb them by multiplication 
with a log-normally distributed random variable with 0.0 mean a standard deviation of 0.5.  The 
perturbations are vertically correlated. Specifically, normal random variables with zero mean and a standard deviation
of 1.0 are generated and then passed through a Gaussian smoothing filter \citep{nixon2019} with a size of two radar bins. The perturbation
vector is then rescaled to have a standard deviation of 0.5.  The perturbations are then exponentiated and multiplied
with the 2C-ICE based $N_w$ values to produce the final $N_w$ values.  The filter size and noise magnitude are chosen
to roughly mimic the observed variability in $N_w$ derived from in situ observations of PSDs, such as those described
in \cite{heymsfield2022impacts}. In addition, we are adding a random noise of
0.0 mean and 0.5 dB standard deviation to the calculated reflectivity values.  Nevertheless, it should be noted that the
uncertainties in the reflectivity calculations are likely to be even larger, given that the SSRGA theory although 
quite accurate cannot possibly capture the entire range of uncertainties in the scattering properties of ice particles.

The lidar observations are computed using the Mie solution included in the scatter-1.1 
package for a backscatter lidar, given that such a lidar is expected to be flown with a 
Ku-band radar and microwave radiometer as part of the NASA Earth System Observatory 
(ESO) Atmosphere Observing System (AOS) in an inclined and/or polar orbit \citep{yorks2022}.
The lidar simulations are idealized in that they do not include random errors due to daytime 
solar background noise or systematic errors such as calibration accuracy or lidar ratio
assumptions. There are three main reasons this approach was taken: (1) it is important to
understand the limitations of combining these three datasets before factoring in 
individual sensor limitations, (2) while more accurate calculations based on more 
realistic ice particle shapes exist, they are rather incomplete and not readily available,
and (3) Wagner and Delene (2022) compared lidar backscatter observations with backscatter 
calculations based on coincident PSD observations and the Mie solution and found good 
agreement, which suggests that electromagnetic properties derived from Mie calculations 
are adequate for practical applications. The lidar molecular backscatter and extinction
are calculated using the lidar module of the CFMIP Observation Simulator Package (COSP; 
Bodas-Salcedo et al. (2011)). COSP simulates the lidar total attenuated backscatter 
signal and scattering ratios at 532 nm for scenes with and without clouds. COSP also 
assumes cloud particles are spherical so that the backscattering phase function is 
estimated based on the effective radius (Mie theory). Despite this assumption, the 
COSP simulations agree well with CALIOP observations. To account for multiple-scattering 
in the lidar observations, we are using the multiscatter-1.2.11 model (Hogan 2015) of 
Hogan and Battaglia (2008).

Shown in Figure 3 are the distributions of simulated Ku-band radar reflectivity and 
lidar backscatter as function of height above the freezing level.
As apparent in the figure, the IWCs associated with detectable Ku-band reflectivity
signal are likely to
occur near mostly around 3.0 km above the freezing level, while the lidar backscatter
distribution exhibits a peak at around 6.0-7.0 km
above the freezing level, which is consistent with the fact the lidar observations
are strongly attenuated in the bottom part of the cloud.

@@

The radiometer observations are calculated using a one-dimensional efficient, but accurate, radiative transfer 
solver based on Eddington's approximation \citep{kummerow1993edd}. The Eddington's approximation has been found to work 
well in cloud and precipitation retrieval application despite its simplicity relative to more general (but also 
computationally intensive) approaches such as Monte Carlo radiative transfer solvers \citep{liu1996three} 
It should be noted tough that the phase functions of ice particles tend to be highly asymmetric at 
sub-millimeter wave frequencies. For radiative transfer solutions based on the Eddington's approximation to be 
accurate, it is necessary that the delta-scaling approach \citep{joseph1976delta} be employed. The delta-scaling 
approach transforms the initial radiative transfer equation into an equivalent one characterized by a less 
asymmetric scattering function and more extinction, which makes the solution Eddington approximation more stable 
and accurate. The absorption due to water vapor and other gases is quantified using the Rosenkranz model 
\citep{rosenkranz1998}.  The water vapor, temperature, and pressure distributions are derived based on a WRF 
simulation of summer convection over the United States.  Specifically, the water vapor, temperature, and 
pressure profiles associated with times and areas where the model produces anvils are selected and clustered 
into 40 classes using the k-Means approach.  The mean extinction profiles at the radiometer frequencies are 
calculated for every class 
and used in process of calculating the brightness temperatures from the estimated ice profiles using a simple 
Monte Carlo procedure.  That is, given a retrieved ice profile and its scattering property, an anvil class 
and its associated absorption, temperature, and pressure profiles are randomly selected and attached to the 
ice scattering properties. To make the procedure physically meaningful, temperature rather than height is 
used in the ice scattering-gas absorption collocation process.  The surface emissivities are randomly chosen between 
0.8 and 1.0 and assumed constant for all radiometer frequencies.  Brightness temperatures are calculated at 
%89-, 183.31 ± 1.1, and 325.15 ± 1.5 GHz,
all frequencies of the 10 channels of the SAPHIR-NG 
radiometer envisioned to be deployed in the AOS mission \citep{brogniez2022time}.  One of the frequencies is 
89-GHz, while the others are centered on the 183.31, and 325.15 GHz water vapor absorption lines. Details are
provided in Table \ref{t_sensors}.

@@

    Instrument & Frequency/Wavelength & Noise & Sensitivity \\
    \hline
    Lidar & 524 nm & LogNormal(0,1) & 5e-7 \\
    \hline
    Radar & 13.8 GHz & 0.5dB & 8 dBZ \\
    \hline
    Radiometer & 89 GHz & 1.0 K & N/A \\
    & 183.31+/-0.2 GHz & 1.0 K & N/A \\
    & 183.31+/-1.1 GHz & 1.0 K & N/A \\
    & 183.31+/-2.8 GHz & 1.0 K & N/A \\
    & 183.31+/-4.2 GHz & 1.0 K & N/A \\
    & 183.31+/-6.8 GHz & 1.0 K & N/A \\
    & 183.31+/-11 GHz & 1.0 K & N/A \\
    & 325.15+/-1.5 GHz & 1.0 K & N/A \\
    & 325.15+/-3.5 GHz & 1.0 K & N/A \\
    & 183.31+/-9.5 GHz & 1.0 K & N/A \\
   \hline \\

@@

\subsection{Synergistic retrievals}

>>>>

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use
normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they 
encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter,
i.e. the 
normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized
PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water 
content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  \cite{testud2001} showed 
that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and 
that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
perfectly explains the relationships between IWC and Z calculated from observed PSDs. 
Although the initial work of \cite{testud2001} was limited to rain and only hinted about the applicability
of the normalization concept to ice observations, subsequent studies showed that parameterizations
of type (\ref{eq:1}) extended to ice \citep{ferreira2001,delanoe2014}.
Equation (\ref{eq:1}) is not 
sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in 
time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function 
of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, 
rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize
$N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}.  
Specifically, we cluster, based on similarity (quantified through the evaluation of the Euclidian distance between profiles), 
a large set 2C-ICE profiles into 18 classes using a k-Means 
procedure. The mean IWC profiles associated with the 18 classes are shown in continuous lines in Figure 1.  
Our estimates, derived using PSD assumptions and electromagnetic scattering calculations that enable 
accurate and physically consistent simulations of radar observations at Ku-band and radiometer observations of 
submillimeter-wave frequencies are also shown in Figure 1. These estimates are based on the self-similarity 
Rayleigh-Gans approximation (SSRGA) of \cite{hogan2017ssrga}. Details regarding the
estimation process are provided in the following paragraphs.  As apparent in Figure 1, the CS and SSRGA estimates are in good 
agreement.  Some discrepancies due to differences between the SSRGA $N_w$ parameterization and the CS 2C-ICE 
"a priori assumptions" are also apparent, but they are not deemed critical in this study, whose objective is 
the investigation of synergistic lidar, Ku-band radar and submillimeter-wave radiometer retrievals, because the 
outcome is not likely to be sensitive to such details.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\textwidth,angle=0]{./Figs/fig01.png}\\
    \caption{Mean CS IWC profiles for 18 classes derived using the k-Means clustering algorithm. For a 
    compressed but intelligible representation, three classes are shown in different colors in each panel.
    The associated 
    mean profiles derived from CS reflectivity observations using the SSRGA scattering calculations 
    and $N_w$ parameterization developed in this study are shown using symbol *. The vertical coordinate 
    is defined relative to the freezing level.}\label{f1}
\end{figure}

@@

For the determination of reference $a$ and $b$ values to be used with Equation (\ref{eq:1}), we assume that 
PSDs are normalized gamma  distributions with $N_w=0.08cm^{-4}$ and $\mu=2$ and calculate 
\begin{equation}
 Z=\frac {\lambda ^4} {\pi ^5 |K_w|^2} \int_0^{\infty} N(D,D_m) \sigma _b(D) dD
\end{equation}
where $\lambda$ is the radar frequency, $|K_w|$ is the dielectric factor of water, $N(D,D_m) dD$ is the number 
of ice particles of diameter with D and D+dD per unit volume, $D_m$ is the mass weighted mean diameter of the 
distribution, and $\sigma _b(D)$ is the backscattering cross-section of ice particle of diameter $D$. The mass 
weighted mean diameter is equidistantly sampled to span the entire range of IWC values in the CS 2C-ICE dataset.
The assumed mass-size relation is that of \cite{brown1995improved} because it works well with the 
SSRGA scattering calculations \citep{heymsfield2022impacts}.  The open source software scatter-1.1 of \citep{scatter-1.1}
is used to provide the actual scattering properties.   
To improve the representation of microphysical variability in the study, we don't assume the values of $N_w$ given
by the 2C-ICE based parametrization described above as the true values. Instead, we perturb them by multiplication 
with a log-normally distributed random variable with 0.0 mean a standard deviation of 0.5.  The 
perturbations are vertically correlated. Specifically, normal random variables with zero mean and a standard deviation
of 1.0 are generated and then passed through a Gaussian smoothing filter \citep{nixon2019} with a size of two radar bins. The perturbation
vector is then rescaled to have a standard deviation of 0.5.  The perturbations are then exponentiated and multiplied
with the 2C-ICE based $N_w$ values to produce the final $N_w$ values.  The filter size and noise magnitude are chosen
to roughly mimic the observed variability in $N_w$ derived from in situ observations of PSDs, such as those described
in \cite{heymsfield2022impacts}. In addition, we are adding a random noise of
0.0 mean and 0.5 dB standard deviation to the calculated reflectivity values, which is consistent with the expected
performance of a space-borne Ku-band radar system \citep{takahashi2008}.  Nevertheless, it should be noted that the
uncertainties in the reflectivity calculations are likely to be even larger, given that the SSRGA theory although 
quite accurate cannot possibly capture the entire range of uncertainties in the scattering properties of ice particles.
Specifically, the SSRGA calculations were carried out assuming ice particles consisting of aggregates of 
bullet rosettes, columnar crystals, and plates.

Moreover, the SSRGA theory was developed for millimeter and 
submillimeter-wave calculations and may not be applicable at lidar's wavelength. 
Therefore, lidar observations are computed using the Mie solution included in the scatter-1.1 
package for a backscatter lidar, given that such a lidar is expected to be flown with a 
Ku-band radar and microwave radiometer as part of the NASA Earth System Observatory 
(ESO) Atmosphere Observing System (AOS) in an inclined and/or polar orbit \citep{yorks2022}.
While uncertainties in the lidar forward model are rather complex and difficult to quantify,
uncertainties in the lidar observations may be accounted for to some extent by including a
multiplicative random noise factor in the calculated lidar backscatter values.  Specifically, the calculated
lidar backscatter values are multiplied with a log-normally distributed random variable with 0.0 mean and a
standard deviation of 0.1.  This results in uncertainties of about 10\% in the lidar backscatter values, which is
consistent the performance of  Cloud-Aerosol Transport System (CATS) lidar system reported in \cite{pauly2019}.  
Nevertheless, the lidar simulations are rather idealized in that they do not include random errors due to daytime 
solar background noise or systematic errors such as calibration accuracy or lidar ratio
assumptions. More advanced models of the observation errors exist \citep{liu2006}, but are not 
considered here. There are three main reasons this approach was taken: (1) it is important to
understand the limitations of combining these three datasets before factoring in 
individual sensor limitations, (2) while more accurate calculations based on more 
realistic ice particle shapes exist, they are rather incomplete and not readily available,
and (3) Wagner and Delene (2022) compared lidar backscatter observations with backscatter 
calculations based on coincident PSD observations and the Mie solution and found good 
agreement, which suggests that electromagnetic properties derived from Mie calculations 
are adequate for practical applications. 
The lidar molecular backscatter and extinction
are calculated using the lidar module of the CFMIP Observation Simulator Package (COSP; 
Bodas-Salcedo et al. (2011)). COSP simulates the lidar total attenuated backscatter 
signal and scattering ratios at 532 nm for scenes with and without clouds. COSP also 
assumes cloud particles are spherical so that the backscattering phase function is 
estimated based on the effective radius (Mie theory). Despite this assumption, the 
COSP simulations agree well with CALIOP observations. To account for multiple-scattering 
in the lidar observations, we are using the multiscatter-1.2.11 model \citep{multiscatter-1.2.11} of 
\cite{hogan2008lidar_ms}.

Shown in Figure 3 are the distributions of simulated Ku-band radar reflectivity and 
lidar backscatter as function of height above the freezing level.
As apparent in the figure, the IWCs associated with detectable Ku-band reflectivity
signal are likely to
occur near mostly around 3.0 km above the freezing level, while the lidar backscatter
distribution exhibits a peak at around 6.0-7.0 km
above the freezing level, which is consistent with the fact the lidar observations
are strongly attenuated in the bottom part of the cloud.  The vertical resolutions of
the radar and lidar observations are the same, i.e. 240 m, and the same as the resolution of the
CS observations upon which they are based. In reality, the radar and lidar observations are likely to have
different vertical resolutions and footprint sizes, which would need to be accounted for in a more 
realistic study.  It should be noted though that the AOS radars and radiometers are expected to achieve
Nyquist sampling, which enables resolution enhancement \citep{early2001image}.  Nevertheless, differences
in the vertical resolutions of the radar and lidar observations and differences in the footprint sizes
may deteriorate the performance of the retrieval algorithm.

@@

The radiometer observations are calculated using a one-dimensional efficient, but accurate, radiative transfer 
solver based on Eddington's approximation \citep{kummerow1993edd}. The Eddington's approximation has been found to work 
well in cloud and precipitation retrieval application despite its simplicity relative to more general (but also 
computationally intensive) approaches such as Monte Carlo radiative transfer solvers \citep{liu1996three} 
It should be noted tough that the phase functions of ice particles tend to be highly asymmetric at 
sub-millimeter wave frequencies. For radiative transfer solutions based on the Eddington's approximation to be 
accurate, it is necessary that the delta-scaling approach \citep{joseph1976delta} be employed. The delta-scaling 
approach transforms the initial radiative transfer equation into an equivalent one characterized by a less 
asymmetric scattering function and more extinction, which makes the solution Eddington approximation more stable 
and accurate. The absorption due to water vapor and other gases is quantified using the Rosenkranz model 
\citep{rosenkranz1998}.  The water vapor, temperature, and pressure distributions are derived based on a WRF 
simulation of summer convection over the United States.  Specifically, the water vapor, temperature, and 
pressure profiles associated with times and areas where the model produces anvils are selected and clustered 
into 40 classes using the k-Means approach.  The mean extinction profiles at the radiometer frequencies are 
calculated for every class 
and used in process of calculating the brightness temperatures from the estimated ice profiles using a simple 
Monte Carlo procedure.  That is, given a retrieved ice profile and its scattering property, an anvil class 
and its associated absorption, temperature, and pressure profiles are randomly selected and attached to the 
ice scattering properties. To make the procedure physically meaningful, temperature rather than height is 
used in the ice scattering-gas absorption collocation process.  The surface emissivities are randomly chosen between 
0.8 and 1.0 and assumed constant for all radiometer frequencies.  Brightness temperatures are calculated at 
%89-, 183.31 ± 1.1, and 325.15 ± 1.5 GHz,
all frequencies of the 10 channels of the SAPHIR-NG 
radiometer envisioned to be deployed in the AOS mission \citep{brogniez2022time}.  One of the frequencies is 
89-GHz, while the others are centered on the 183.31, and 325.15 GHz water vapor absorption lines. Details are
provided in Table \ref{t_sensors}.  Errors in the radiometer observations are modeled assuming a 
Noise-Equivalent-Delta-T (NEDT) of 1K, which is a readily achievable level for modern satellite radiometers \cite{draper2015}.

@@

    Instrument & Frequency/Wavelength & Noise Assumptions& Sensitivity \\
    \hline
    Lidar & 524 nm & LogNormal(0,0.1) & 5e-7 m$^{-1}$sr$^{-1}$ \\
    \hline
    Radar & 13.8 GHz & 0.5dB & 8 dBZ \\
    \hline
    Radiometer & 89 GHz & 1.0 K & N/A \\
    & 183.31+/-0.2 GHz & 1.0 K & N/A \\
    & 183.31+/-1.1 GHz & 1.0 K & N/A \\
    & 183.31+/-2.8 GHz & 1.0 K & N/A \\
    & 183.31+/-4.2 GHz & 1.0 K & N/A \\
    & 183.31+/-6.8 GHz & 1.0 K & N/A \\
    & 183.31+/-11 GHz & 1.0 K & N/A \\
    & 325.15+/-1.5 GHz & 1.0 K & N/A \\
    & 325.15+/-3.5 GHz & 1.0 K & N/A \\
    & 183.31+/-9.5 GHz & 1.0 K & N/A \\
   \hline \\

@@

\subsection{Active instrument retrievals}
Although retrievals from the lidar-only or radar-only observations are not expected to be as accurate as those from
radiometer-only observations, the lidar observations being subject to severe attenuation while the radar observations
being limited by its sensitivity, they are nevertheless insightful.
\subsection{Synergistic retrievals}
